\documentclass[a4paper, 11pt]{article}
% MLA format
\usepackage[letterpaper]{geometry}
%\usepackage{times}
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{} 
\chead{} 
\rhead{Simmons \thepage} 
\lfoot{} 
\cfoot{} 
\rfoot{}
\renewcommand{\headrulewidth}{0pt} 
\renewcommand{\footrulewidth}{0pt} 

%\usepackage{mdwlist}
\usepackage{enumitem}
\setlist{  
  listparindent=\parindent,
  parsep=0pt,
}
\title{Homework 10}
\author{Mark Simmons}
\date{May 1, 2020}


% Typing in IPA
\usepackage{tipa}

% Sentence trees
\usepackage{tikz}
\usepackage{tikz-qtree}
\usepackage{lscape}
\usepackage{graphicx}
\usepackage{pstricks}
\usepackage{tree-dvips}
\tikzset{level distance=30pt,
sibling distance=6pt,
every tree node/.style={align=center},
}

% Glosses
\usepackage{linguex}

\begin{document}

\maketitle



\begin{enumerate}[label=\textbf{\arabic*.}]

\item Short Answer

\begin{enumerate}[label=(\alph*)]

\item Mary \textbf{is eager} to leave the country.\\
  This sentence features subject control, which we can tell since the sentence does not accept expletive
  insertion 
  (Mary is eager to leave the country =/= It is eager for Mary to leave the country)
  nor passive raising
  (Mary is eager to leave the country =/= The country is eager to be left by Mary.)

  \item Bill \textbf{imagined} Kim to have won the race.\\
  This sentence features subject to object raising, which we can tell since the sentence does accept
  passive raising
  (Bill imagined Kim to have won the race = Kim was imagined to have won the race by Bill)
  and insertion of an expletive object
  (Bill imagined it that Kim had won the race)

  \item Fred \textbf{forced} Kim to watch the movie.\\
  This sentence features object control, which we can tell since the sentence does not accept
  passive raising
  (Fred forced the movie to be watched by Kim =/= Fred forced Kim to watch the movie)
  nor does it allow an idiomatic phrase to be placed in the embedded clause
  (Fred forced the cat to be let out of the bag).

  \item John \textbf{is certain} to win the race.
  This sentence features subject to subject raising, which we can tell because it accepts expletive insertion
  (It is certain that John will win the race = John is certain to win the race) and passive raising
  (The race is certain to be won by John == John is certain to win the race)

\end{enumerate}

\item Argumentation

  In generative grammar, embedded clauses with no overt subject have a phonologically null
  element occupying subject position. This element is either a trace, which indicates that
  the subject in matrix clause originates in the embedded clause in deep structure (DS), or
  it is PRO, a phonologically null determiner phrase (DP) that originates and stays within the
  embedded clause, and is coindexed with the subject of the matrix clause.

  \ex.
    \a. John$_{i}$ seemed [\textsc{cp} $t_{i}$ to $t_{i}$ leave ].
    \b. John$_{i}$ hoped [\textsc{cp} PRO$_{i}$ to $t_{i}$ leave ].

  In (1a), \emph{John} is located where the second trace is in DS, whereas in (1b) \emph{John}
  is in the matrix clause in both DS and SS, and the element PRO moves up across the T \emph{to}
  to the specifier-TP position within the embedded clause.

  The concept of PRO is motivated by the $\theta$-Criterion, which states that every DP can only
  be assigned a single $\theta$-Role by a verb. In (1a), \emph{seem} does not assign a $\theta$-
  role, thus it lacks a subject and requires \emph{John} to raise from the embedded clause to 
  satisfy the EPP.
  For (1b), however, \emph{hope} and \emph{leave} both assign $\theta$-roles to their
  subjects, thus for \emph{John} to occupy subject position in the matrix clause, the embedded
  clause needs a DP capable of taking the $\theta$-role given by \emph{leave}. A sentence where
  verbs in multiple clauses each assign $\theta$-roles to the same semantic subject is said to
  exhibit Control.
  
  If we merely revise the $\theta$-Criterion to allow for DP's to receive multiple $\theta$-
  roles, it is no longer necessary to posit PRO, we can generate (1b) only with movement.

  \ex. John$_{i}$ hoped [\textsc{cp} $t_{i}$ to $t_{i}$ leave ].

  Where \emph{John} receives $\theta$-roles from both \emph{leave} and \emph{hope}.

  In this paper, I propose that it is preferable to maintain the $\theta$-Criterion as is,
  and thus keep the PRO subject in the embedded clause. I argue this from data on case
  agreement in Icelandic. In the following examples, \emph{EC} refers to an `empty category'
  occupied either by a trace or PRO element.

  \ex.
    \ag. Strákarna$_{i}$ vir\textipa{D}ast 
    [ EC$_{i}$  vanta eikki alla í skólann ].\\
    the-boys\textsc{.acc} seem {} {} lack not all\textsc{.acc} in the-school\\
    \trans 'The boys seem not to be all absent from school.'
    \bg. Strákarnir$_{i}$ vonast til
    [ a\textipa{D} EC$_{i}$  vanta eikki alla í skólann ].\\
    the-boys\textsc{.nom} hope for {} to {} lack not all\textsc{.acc} in the-school\\
    \trans 'The boys hope not to be all absent from school.'

  Note the parallelism between (3a,b) and (1a,b) - the only difference between each pair of
  sentences is the verb in the matrix clause- \emph{seem/vir\textipa{D}ast} in (1a, 3a), which does not assign
  a $\theta$-role to the subject, and \emph{hope/vonast} in (1b, 3b), which does. Thus, (3a)
  is a canonical instance of subject-to-subject raising, while (3b) is an instance of subject control.
  I will argue that our model can only generate both of these sentences if we assume a
  phonologically null PRO element in (3b) where \emph{EC} is placed, rather than a trace from
  a raised subject.

  The verb in the embedded clause, \emph{vanta} `lack', takes an accusative quirky
  subject. For this reason the quantifier \emph{alla} bears accusative case within the
  embedded clause of both sentences.

  If we assume that the subject of the matrix clause originates as subject of the embedded clause
  in DS, we would expect that \emph{vanta} assigns it accusative case, and that it would
  maintain accusative case when raised.

  \ex.
  \ag. Strákarna$_{i}$ vir\textipa{D}ast 
  [ t$_{[+ACC]i}$  vanta eikki alla í skólann ].\\
  the-boys\textsc{.acc} seem {} {} lack not all\textsc{.acc} in the-school\\
  \trans 'The boys seem not to be all absent from school.'
  \bg. *Strákarna$_{i}$ vonast til
  [ a\textipa{D} t$_{[+ACC]i}$  vanta eikki alla í skólann ].\\
  the-boys\textsc{.acc} hope for {} to {} lack not all\textsc{.acc} in the-school\\
  \trans Intended: 'The boys hopenot to be all absent from school.' 
  
  This explains why \emph{strákarna} is accusative in (3a). However, if we assume that
  (3b) features subject raising alone (and not control), then our model incorrectly generates
  the ungrammatical sentence (4b). If we assume that (4b) features control and thus the subject
  of the embedded clause is the null element PRO, we predict the grammatical sentence (5).

  \exg. Strákarnir$_{i}$ vonast til
  [ a\textipa{D} PRO$_{[+ACC]i}$  vanta eikki alla í skólann ].\\
  the-boys\textsc{.nom} hope for {} to {} lack not all\textsc{.acc} in the-school\\
  \trans 'The boys hope not to be all absent from school.'

  Since \emph{strákarnir} originates in the matrix clause, it is never assigned accusative
  case by \emph{vanta}. Instead, \emph{vanta} assigns accusative to PRO, which is not
  reflected overtly in the sentence, but nevertheless gives accusative case to the quantifier
  \emph{alla} which agrees with it morphologically.

  Thus, because embedded verbs in Icelandic trigger quirky case on subjects in the matrix
  clause only in sentences with Control, we must analyze these sentences differently
  with regards to syntax than sentences without Control. In other words, subject-raising
  cannot explain the patterns observed in Icelandic Control constructions, though if we posit
  the phonologically null DP PRO, we can explain the observed data consistently.

%\pagebreak

\item Technical

  \begin{enumerate}[label=(\alph*)]

	% Kim tried to be offended.
	\item Deep Structure\\
	\bigskip
	\leavevmode\vadjust{\vspace{-\baselineskip}}\newline
	%\begin{landscape}
	\noindent{\begin{tikzpicture}
	{\small \Tree
	[.CP {}
	[.C' C\\$\emptyset_{[-Q]}$
	[.TP {}
  [.T' T\\-ed
  [.VP [.DP$_{i}$ \edge[roof]; \node(specTP){Kim}; ]
  [.V' \node(v){V\\try};
    [.CP {}
    [.C' C\\$\emptyset_{[-Q]}$
    [.TP {}
    [.T' T\\to
      [.VP {}
      [.V' V\\be
        [.VP {}
        [.V' V\\offended [.DP$_{i}$ \edge[roof]; \node(specToBeOffended){PRO}; ]
        ]%V'
        ]%VP
      ]%V'
      ]%VP
    ]
    ]%TP
    ]%C'
    ]%CP
  ]%V'
  ]%VP
	]%T'
	]%TP
	]%C'
	]%CP
	}
	\end{tikzpicture}}

	\pagebreak

	% Kim tried to be offended.
  \noindent Surface Structure\\
	\bigskip
	\leavevmode\vadjust{\vspace{-\baselineskip}}\newline
	%\begin{landscape}
	\noindent{\begin{tikzpicture}
	{\small \Tree
	[.CP {}
	[.C' C\\$\emptyset_{[-Q]}$
	[.TP [.DP$_{i}$ \edge[roof]; \node(specTP){Kim}; ]
  [.T' \node(traceT){T};
  [.VP \node(specTry){t$_{i}$};
  [.V' \node(v){V\\try-ed};
    [.CP {}
    [.C' C\\$\emptyset_{[-Q]}$
    [.TP [.DP$_{i}$ \edge[roof]; \node(specToBeOffended){PRO}; ]
    [.T' T\\to
      [.VP {}
      [.V' V\\be
        [.VP {}
        [.V' V\\offended \node(specOffend){t$_{i}$};
        ]%V'
        ]%VP
      ]%V'
      ]%VP
    ]
    ]%TP
    ]%C'
    ]%CP
  ]%V'
  ]%VP
	]%T'
	]%TP
	]%C'
	]%CP
	}
	\draw[dashed,->] (traceT)..controls +(south:3) and +(south:3)..(v);
  \draw[semithick,->] (specTry)..controls +(south:2) and +(south:2)..(specTP);
	\draw[semithick,->] (specOffend)..controls +(south:5) and +(south:5)..(specToBeOffended);


  \end{tikzpicture}}

  \pagebreak

  \tikzset{level distance=15pt,
  sibling distance=3pt,
  }

  % I persuaded Kim to want to walk my dog.
	\item Deep Structure\\
	\bigskip
	\leavevmode\vadjust{\vspace{-\baselineskip}}\newline
	%\begin{landscape}
	\noindent{\begin{tikzpicture}
  {\tiny \Tree
  [.CP {}
  [.C' C\\$\emptyset_{[-Q]}$
  [.TP {}
  [.T' \node(traceT){T\\-ed};
  [.VP [.DP$_{i}$ \edge[roof]; \node(specTP){I}; ]
  [.V' \node(v){V\\persuade}; [.DP \edge[roof]; Kim$_{j}$ ]
    [.CP {} %{PRO} to want
    [.C' C\\$\emptyset_{[-Q]}$
    [.TP {}
    [.T' T\\to
      [.VP [.DP$_{j}$ \edge[roof]; \node(specToWant){PRO}; ]
      [.V' V\\want
      [.CP {} %{PRO} to walk my dog
      [.C' C\\$\emptyset_{[-Q]}$
      [.TP {}
      [.T' T\\to
      [.VP [.DP$_{j}$ \edge[roof]; \node(specToWalk){PRO}; ]
      [.V' V\\walk [.DP \edge[roof]; {my dog} ]
      ]%V'
      ]%VP
      ]%T'
      ]%TP
      ]%C'
      ]%CP
      ]%V'
      ]%VP
    ]
    ]%TP
    ]%C'
    ]%CP
  ]%V'
  ]%VP
  ]%T'
  ]%TP
  ]%C'
  ]%CP
  }
	\end{tikzpicture}}


  % I persuaded Kim to want to walk my dog.
  \noindent Surface Structure\\
	\bigskip
	\leavevmode\vadjust{\vspace{-\baselineskip}}\newline
	%\begin{landscape}
	\noindent{\begin{tikzpicture}
	{\tiny \Tree
	[.CP {}
	[.C' C\\$\emptyset_{[-Q]}$
	[.TP [.DP$_{i}$ \edge[roof]; \node(specTP){I}; ]
  [.T' \node(traceT){T};
  [.VP \node(specTry){t$_{i}$};
  [.V' \node(v){V\\persuade-ed}; [.DP \edge[roof]; Kim$_{j}$ ]
    [.CP {} %{PRO} to want
    [.C' C\\$\emptyset_{[-Q]}$
    [.TP [.DP$_{j}$ \edge[roof]; \node(specToWant){PRO}; ]
    [.T' T\\to
      [.VP \node(specWant){t$_{j}$};
      [.V' V\\want
      [.CP {} %{PRO} to walk my dog
      [.C' C\\$\emptyset_{[-Q]}$
      [.TP [.DP$_{j}$ \edge[roof]; \node(specToWalk){PRO}; ]
      [.T' T\\to
      [.VP \node(specWalk){t$_{j}$};
      [.V' V\\walk [.DP \edge[roof]; {my dog} ]
      ]%V'
      ]%VP
      ]%T'
      ]%TP
      ]%C'
      ]%CP
      ]%V'
      ]%VP
    ]
    ]%TP
    ]%C'
    ]%CP
  ]%V'
  ]%VP
	]%T'
	]%TP
	]%C'
	]%CP
	}
	\draw[dashed,->] (traceT)..controls +(south:2) and +(south:2)..(v);
  \draw[semithick,->] (specTry)..controls +(south:1) and +(south:1)..(specTP);
  \draw[semithick,->] (specWant)..controls +(south:1) and +(south:1)..(specToWant);
	\draw[semithick,->] (specWalk)..controls +(south:1) and +(south:1)..(specToWalk);


  \end{tikzpicture}}

  \pagebreak
  
  % I persuaded Kim to appear to walk my dog.
	\item Deep Structure\\
	\bigskip
	\leavevmode\vadjust{\vspace{-\baselineskip}}\newline
	%\begin{landscape}
	\noindent{\begin{tikzpicture}
  {\tiny \Tree
  [.CP {}
  [.C' C\\$\emptyset_{[-Q]}$
  [.TP {}
  [.T' \node(traceT){T\\-ed};
  [.VP [.DP$_{i}$ \edge[roof]; \node(specTP){I}; ]
  [.V' \node(v){V\\persuade}; [.DP \edge[roof]; Kim$_{j}$ ]
    [.CP {} %{PRO} to want
    [.C' C\\$\emptyset_{[-Q]}$
    [.TP {}
    [.T' T\\to
      [.VP {}
      [.V' V\\appear
      [.CP {} %{PRO} to walk my dog
      [.C' C\\$\emptyset_{[-Q]}$
      [.TP {}
      [.T' T\\to
      [.VP [.DP$_{j}$ \edge[roof]; \node(specToWalk){PRO}; ]
      [.V' V\\walk [.DP \edge[roof]; {my dog} ]
      ]%V'
      ]%VP
      ]%T'
      ]%TP
      ]%C'
      ]%CP
      ]%V'
      ]%VP
    ]
    ]%TP
    ]%C'
    ]%CP
  ]%V'
  ]%VP
  ]%T'
  ]%TP
  ]%C'
  ]%CP
  }
	\end{tikzpicture}}


  % I persuaded Kim to appear to walk my dog.
  \noindent Surface Structure\\
	\bigskip
	\leavevmode\vadjust{\vspace{-\baselineskip}}\newline
	%\begin{landscape}
	\noindent{\begin{tikzpicture}
	{\tiny \Tree
	[.CP {}
	[.C' C\\$\emptyset_{[-Q]}$
	[.TP [.DP$_{i}$ \edge[roof]; \node(specTP){I}; ]
  [.T' \node(traceT){T};
  [.VP \node(specTry){t$_{i}$};
  [.V' \node(v){V\\persuade-ed}; [.DP \edge[roof]; Kim$_{j}$ ]
    [.CP {} %{PRO} to want
    [.C' C\\$\emptyset_{[-Q]}$
    [.TP [.DP$_{j}$ \edge[roof]; \node(specToAppear){PRO}; ]
    [.T' T\\to
      [.VP {}
      [.V' V\\appear
      [.CP {} %{PRO} to walk my dog
      [.C' C\\$\emptyset_{[-Q]}$
      [.TP \node(specToWalk){t$_{j}$};
      [.T' T\\to
      [.VP \node(specWalk){t$_{j}$};
      [.V' V\\walk [.DP \edge[roof]; {my dog} ]
      ]%V'
      ]%VP
      ]%T'
      ]%TP
      ]%C'
      ]%CP
      ]%V'
      ]%VP
    ]
    ]%TP
    ]%C'
    ]%CP
  ]%V'
  ]%VP
	]%T'
	]%TP
	]%C'
	]%CP
	}
	\draw[dashed,->] (traceT)..controls +(south:2) and +(south:2)..(v);
  \draw[semithick,->] (specTry)..controls +(south:1) and +(south:1)..(specTP);
  \draw[semithick,->] (specWalk)..controls +(south:1) and +(south:1)..(specToWalk);
  \draw[semithick,->] (specToWalk)..controls +(south:2) and +(south:2)..(specToAppear);


  \end{tikzpicture}}

  \pagebreak

  \tikzset{level distance=30pt,
  sibling distance=6pt,
  }

  % We will hope for him to return.
	\item Deep Structure\\
	\bigskip
	\leavevmode\vadjust{\vspace{-\baselineskip}}\newline
	%\begin{landscape}
	\noindent{\begin{tikzpicture}
	{\small \Tree
    [.CP {}
    [.C' C\\$\emptyset_{[-Q]}$
    [.TP {}
    [.T' T\\will
    [.VP [.DP$_{i}$ \edge[roof]; \node(specTP){We}; ]
    [.V' V\\hope
      [.CP {}
      [.C' C\\for
      [.TP {}
      [.T' T\\to
        [.VP [.DP$_{j}$ \edge[roof]; \node(specToReturn){him}; ]
        [.V' V\\return. {}
        ]%V'
        ]%VP
      ]
      ]%TP
      ]%C'
      ]%CP
    ]%V'
    ]%VP
    ]%T'
    ]%TP
    ]%C'
    ]%CP
    }
	\end{tikzpicture}}

	\pagebreak

	% We will hope for him to return.
  \noindent Surface Structure\\
	\bigskip
	\leavevmode\vadjust{\vspace{-\baselineskip}}\newline
	%\begin{landscape}
	\noindent{\begin{tikzpicture}
	{\small \Tree
	[.CP {}
	[.C' C\\$\emptyset_{[-Q]}$
	[.TP [.DP$_{i}$ \edge[roof]; \node(specTP){We}; ]
  [.T' T\\will
  [.VP \node(specTry){t$_{i}$};
  [.V' V\\hope
    [.CP {}
    [.C' C\\for
    [.TP [.DP$_{j}$ \edge[roof]; \node(specToReturn){him}; ]
    [.T' T\\to
      [.VP \node(specReturn){t$_{j}$};
      [.V' V\\return. {}
      ]%V'
      ]%VP
    ]
    ]%TP
    ]%C'
    ]%CP
  ]%V'
  ]%VP
	]%T'
	]%TP
	]%C'
	]%CP
	}
  \draw[semithick,->] (specTry)..controls +(south:2) and +(south:2)..(specTP);
	\draw[semithick,->] (specReturn)..controls +(south:2) and +(south:2)..(specToReturn);


  \end{tikzpicture}}

  \end{enumerate}

\end{enumerate}

\end{document}